Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-19 paper/ijcai/paper.tex
pass on abstract (please check)

\begin{abstract}
Several approaches have been proposed to improve automated software fault
diagnosis, aiming to reduce the effort and costs spent in debugging. 
Dynamic Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are very popular techniques and normally seen as complementary. However, this combination has not been entirely explored yet.
Thus, this paper reports the outcome of an empirical study
performed to demystify the impact of combining \ds{} with \sfl{}, a technique we coin as Tandem-FL. 
We
suspect that several highly suspicious components --- often involved in failing, 
but seldom in passed executions ---
may be unrelated to the bug. 
This study also discusses on limitations of dynamic slicing, such as the potential
of missing faulty statements. Our
results show that combining SFL with dynamic slicing improves the diagnostic
accuracy in \Rui{x\% on average}, hence leading to the root cause of observed failures faster.
\end{abstract}

>>>>

\begin{abstract}
Several approaches have been proposed in the literature to improve
debugging costs through automated software fault diagnosis.  Dynamic
Slicing (\ds{}) and Spectrum-based Fault Localization (\sfl{}) are
very popular fault diagnosis techniques and normally seen as
complementary.  This paper reports the outcome of a comprehensive
study with the goal of demystifying the impact of combining \ds{} with
\sfl{}.  We suspect that several highly suspicious components---often
involved in failing, but seldom in passing executions---may be
unrelated to the bug. With the aforementioned combination, such
components could be identified and their suspiciousness reduced.  This
study also discusses the impact of the dynamic slicing key
limitation---the risk of missing faulty statements. Our results show
that, in practice, \ds{} rarely misses faulty statements (\Fix{X}
misses in \Fix{Y} cases) and that the \ds{}-\sfl{} combination
improves the diagnostic accuracy in \Rui{x\% on average}. \Mar{check
  if you agree on this...} To sum, we found that, despite tacit
opinions of the reserach commuinity about the usefulness of \ds{} in
automated debugging, we found the combination practical and effective,
and encourage new \sfl{} techniques to be evaluated against that
optimization.
%, a technique we coin as Tandem-FL
%% hence leading to the root cause of
%% observed failures faster.
\end{abstract}
